---
title: "hw1_p8105_js5958"
output: github_document
date: "2022-09-24"
---

```{r}
library(tidyverse)
library(ggplot2)

```

## Problem 1
```{r cars}
data("penguins", package = "palmerpenguins")
```

a) The important variables are *`r names(penguins)`*.

b) The number of **rows** in the penguins data set is **`r nrow(penguins)`**.

c) The number of **columns** in the penguins data set is **`r ncol(penguins)`**.

d) The unique **species** in the penguins data set are **`r unique(pull(penguins, species))`**.

e) The unique **island** in the penguins data set are **`r unique(pull(penguins, island))`**.

f) The unique **years** in the penguins data set are **`r unique(pull(penguins, year), na.rm = TRUE)`**.

g) The **sex** in the penguins data set are **`r unique(na.omit(pull(penguins, sex)))`**.

j) 
The mean of the **flipper length** is *`r round(mean(pull(penguins, flipper_length_mm),na.rm = TRUE))`*mm.
The standard deviation of the flipper length is  *`r round(sd(pull(penguins, flipper_length_mm), na.rm = TRUE), digits=2)`*.

### First time creating scatterplot for this class 
```{r Creating scatterplot, message = FALSE, warning = FALSE}
penguin_scatterplot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(shape = penguins$species, size = 3) +
  ggtitle("Flipper Length vs Bill Length") + theme(plot.title = element_text(hjust = 0.5))

penguin_scatterplot
```

### Saving my first ggplot (scatterplot) as PDF
```{r Saving ggplot as PDF, message = FALSE, warning = FALSE}
ggsave("scatter_plot.pdf", plot = penguin_scatterplot, height = 4, width = 6)
```


```{r Creating a dataframe}

set.seed(102102)

df_main <- tibble(
                  random_sample = rnorm(10),
                  logical_vector = random_sample > 0,
                  character_vector = c("I", "go", "to", "lake", "the", "lake", "everyday", "to","just", "chill"),
                  factor_vector = factor(c("positve", "negative", "neutral", "positve", "negative", "negative", "neutral", "postive", "neutral", "negative")),
)

knitr::kable(df_main)

df_main
```

```{r}
numeric_char = as.numeric(pull(df_main,character_vector))
numeric_logv = as.numeric(pull(df_main,logical_vector))
numeric_fac = as.numeric(pull(df_main, factor_vector))
```


## Calculating the mean of the newly converted numeric variables 

```{r}
mean_numchar = mean(numeric_char)
mean_numlogic = mean(numeric_logv)
mean_numfactor = mean(numeric_fac)
mean_numchar
```


```{r}
numeric_factorvec = as.numeric(as.character(pull(my, fac_vec)))
```
